Abstracts of JSS papers
========================================================

# Abstract
This document demonstrates the usage of the Topicmodels package to analyse a document-collection as described by Grün and Hornik (2011).

# Do the work

## Preparation

Install the needed packages. The corpus to be analysed is available as R package:

```{r}
install.packages("corpus.JSS.papers",
  repos = "http://datacube.wu.ac.at/", type = "source")
```

Install other packages:

```{r}
install.packages('topicmodels')
install.packages('tm')
install.packages('XML')
```

```{r}
library('topicmodels')
library('XML')
library('slam')
```

```{r}
remove_HTML_markup <- function(s) tryCatch({
    doc <- htmlTreeParse(paste("<!DOCTYPE html>", s),
    asText = TRUE, trim = FALSE)
    xmlValue(xmlRoot(doc))
}, error = function(s) s)
```


Load the corpus:

```{r}
data("JSS_papers", package = "corpus.JSS.papers")
```

Select the abstracts up to august 5, 2005 and omit the papers that contain funny characters:

```{r}
JSS_papers <- JSS_papers[JSS_papers[,"date"] < "2010-08-05",]
JSS_papers <- JSS_papers[sapply(JSS_papers[, "description"], Encoding) == "unknown",]
```

```{r}
Sys.setlocale("LC_COLLATE", "C")
```


```{r}
JSS_dtm <- DocumentTermMatrix(
            corpus,
            control = list( stemming = TRUE
			              , stopwords = TRUE
						  , minWordLength = 3
						  , removeNumbers = TRUE
						  , removePunctuation = TRUE
						  )
		   )
dim(JSS_dtm)
```

```{r}
summary(col_sums(JSS_dtm))
```



# References


* Bettina Grün and Kurt Hornik (2011): "topicmodels: An R package for Fitting Topic Models." Journal of Statistical    Software 40(13). URL: [Original paper](http://www.jstatsoft.org/v40/i13/);  [Modified/shortened version on Rcran](http://cran.r-project.org/web/packages/topicmodels/vignettes/topicmodels.pdf) 
